Conference Paper Critique

### 2019-03-27 conf_paper/paper.tex
fdsjkl

The technical motivation underlying this paper is the creation of an Field Programmable Gate Array (FPGA) based prototyping platform for All Digital Phase Lock Loop (ADPLL) networks. As the creation of Application Specific Integrated Circuits (ASICs) is an expensive and time consuming process, any mistake has the potential to be rather costly. As such, prior to the manufacture of an IC, it is important to ensure that any errors made in the design have been weeded out.

@@

\section{System Architecture}
An ADPLL network, as the name would suggest, is created from a number of ADPLLs that are coupled using digital phase comparators which attempt to measure the phase error between two oscillators, with each non edge node being connected to four neighbours. Figure \ref{fig:adpll_network} illustrates such a system on a small scale, with a number of ADPLLs laid out in a Cartesian grid. The individual ADPLLs, often called distributed ADPLLs as the phase detectors are shared between nodes, are made up of a digitally controllable oscillator, an error combination block and a digital loop filter with the aforementioned digital phase detectors lying between each pair of oscillators.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.25\textwidth]{adpll_network}
    \caption{ADPLL Network Architecture.}
    \label{fig:adpll_network}
    \vspace{0.5cm}
    \includegraphics[width=0.4\textwidth]{dist_adpll}
    \caption{Distributed ADPLL Design.}
    \label{fig:adpll_base}
    \vspace{-0.5cm}
\end{figure}
\subsection{Digitally Controlled Oscillators}
While regular Voltage Controlled Oscillator (VCO) is tuned by the input voltage over a continuous range of values, in a digital system there are a very limited number of voltages representable, most commonly just two levels. As such, using the voltage itself to control an oscillator is not a viable strategy and instead Digitally, or as they are sometimes known as Numerically, Controlled Oscillators (DCO) accept an \textit{n} bit wide control signal that alters the period of the output waveform. While tuning range, centre frequency and linearity apply as in a VCO, a DCO also has a minimum frequency step as a result of the non continuous control values. %TODO WORDING
In combination with the bit width of the control signal, the minimum frequency step limits the range over which the oscillator can be tuned. Frequently the output of the DCO is divided down to allow the control blocks in the feedback path that are clocked on this signal, to run at a lower and thus easier frequency.
\subsection{Loop Filter}
The loop filter is a key aspect of a phase lock loop as without it only the current output of the phase detector could be used to compute the control voltage of the VCO.
In an ADPLL it performs an identical role however, the digital environment results the traditional loop filter being replaced by a discrete time Proportional Integral (PI) controller, with the integral path of the controller implemented by an accumulator.
\subsection{Error Combiner}
The Error Combiner, as the name suggests, performs a summation of the error signals from the phase detectors lying between any neighbouring oscillator and its neighbours. It is often convenient for this to be performed as a weighted sum, thus avoiding different gain requirements for the loop filter of oscillators in the corners of the grid that only have a pair of neighbours. The ability to change the weights during operation enables ``uni-directional start-up'', which Javiden et. al \cite{javidan2011all} found prevented the system from entering unwanted stable equilibriums warned of in Pratt and Nguyen's seminal paper.
\subsection{Phase Detector}
As in a conventional PLL the phase detector outputs a value proportional to the difference in phase between a pair of signals, which is then output as a continuous voltage.
A digital phase detector then attempts to do the same by measuring the difference between fixed reference points in the waveform, which as a digital system deals with square waves, this is typically the rising edge of each input to the block.
Similarly to the oscillator, quantisation also plays a role in the behaviour of this block, with the time difference between each rising edge having a minimum possible measurement step.
In distributed ADPLLs the phase detector has dual outputs, each the inverse of the other, in order to feed the correct value to both of the connected error combiners.

\section{FPGA Prototyping}
\subsection{FPGA Restrictions}
The use of an FPGA comes with many restrictions as to how a complex system such as an ADPLL can be designed with the mixed signal blocks, the DCO and phase detectors in particular being curtailed by the lack of transistor level control of the design and layout.\\
Two potential solutions exist which alleviate this problem, and are suited to different frequency ranges and/or goals of the designer. Firstly the clock signal generated by the FPGA's clock distribution block can be used to drive accumulator based oscillators and phase detectors, a technique suitable in two main use cases: The emulation of the performance of an already designed system operating at a proportionally cut down frequency. At frequencies that are orders of magnitude lower than the maximum obtainable clock frequency of the FPGA's clock manager.
The downside of this approach is that the minimum steps are dictated by the clock frequency of the FPGA, which at frequencies that are not orders of magnitude lower than the FPGA clock will result in coarse resolutions for detector or oscillator, and thus greater jitter seen at the oscillator output.\\
The second solution to the problem is more akin to the real world system, and uses the delay through primitive elements such as inverters, which can be deduced from measurements on the FPGA of choice but will vary depending on the layout selected. In the case of the FPGA used for this paper, a Xilinx Artix-7 (XC7A100T-1CSG324C), this delay is in the region of 300 picoseconds but varies depending on the routing between elements. This design is better suited to scenarios where the desired operating frequency is a significant fraction of the maximum usable clock of the FPGA or it is particularly desirable to have asynchronous behaviour in the system as in an ASIC. It is not suited to lower frequency designs as the number of inverters required will run into spacial constraints.
\subsection{Digitally Controlled Oscillators on an FPGA}
There are three key designs that be used to implement a DCO on an FPGA, two of which rely on the FPGA clock and one using inverter primitives. Each of these designs fulfil a different role in mimicking the behaviour of an ASIC based mixed signal DCO.

@@

\subsection{Phase Detectors on an FPGA}
The two options for replicating the behaviour of a phase detector also employ the same two design principles, with the option better suited to lower frequency signals once again, being driven by the clock generated by the FPGA and an inverter based design better suiting higher frequency systems, where the greater resolution offered is beneficial.\\
A  Sign-Number (SigNum) detector is a common method of performing phase-frequency detection in an ADPLL and is the method that will be discussed in this paper. As the name suggests, this design constitutes two sections, with one determining the sign of the phase difference and the other, its magnitude. The first issue with implementing a phase detector on an FPGA is the issue of metastability, where the output of a circuit element is at an undetermined level, which can occur if both signs were to have edges within a short time of another or the set-up/hold times of a register are violated. This issue is easily addressed in an ASIC with an arbiter, however, an arbiter is a mixed signal circuit that is not synthesisable on an FPGA.

\subsubsection*{Design A}
The first potential design uses a Finite State Machine (FSM) to determine which edge has occurred first and thus the sign, and a counter that computes the time difference between each rising edge. This counter is clocked by the FPGA clock, thus giving the system a time resolution of $\frac{1}{F_{\textrm{FPGA}}}$. As with the FPGA driven oscillator, this results in a design that is only suitable when the frequency of operation is well below that of the FPGA clock due to resolution constraints. In order to avoid the problem of metastability, the incoming waveforms can be synchronised to the clock of the FPGA for no penalty beyond the extra clock cycle taken, as this synchronisation performs the same quantisation that would otherwise have occurred in the counter measuring the time difference. This design is better suited for use with the accumulator based oscillators due to the overlapping suitable frequency ranges, however, it can also be used in conjunction with an inverter ring. Important to note is that in the case of the Artix-7 used in this paper, this results in a four times worse phase difference resolution than period resolution which made low jitter operation difficult, but this combination could be made possible by removing eight rather than two inverters for each control code step. %TODO plot this later

\subsubsection*{Design B}
Better suited for use with the inverter based oscillator, is a system that mimics the behaviour of a tapped delay line, working asynchronously to the FPGA clock. As the FPGA clock is not used, and that of the ADPLL cannot be used to measure itself, an unclocked sign detection circuit is required, an example of which can be seen in Figure \ref{fig:segn_pdetdl}. This is nearly identical to sign detection methods used on an ASIC, with the arbitration circuit replaced by a second SR Latch, which alleviates the issue of metastability.\\
A tapped delay line can be emulated on an FPGA through the use of inverter pairs, due to their short and approximately known delay placed between each tap.
The resolution then is the propagation time through the pair, although this will once again depend on the layout specifics, which was approximately 600 picoseconds on an Artix-7. This is significantly lower than the 4 nanoseconds achieved using the previous design and thus more suitable for use with an inverter ring oscillator, as this resolution is better than the time resolution of the oscillator. Figure \ref{fig:num_pdetdl} illustrates the configuration of the circuit used to emulate the function of a delay line that will be used in this paper.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{../new_pdet1}
    \caption{Design B Sign Detection RTL Diagram.}
    \label{fig:segn_pdetdl}
    \vspace{-0.5cm}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{../new_pdet2}
    \caption{Tapped Delay Line Emulation RTL Diagram.}
    \label{fig:num_pdetdl}
    \vspace{-0.5cm}
\end{figure}
\section{Comparison of Designs}
This paper will now examine the performance of a number of combinations of these blocks and the performance thereof, specifically oscillator 1 with phase detector A and oscillator 2 with detectors A \& B. For each test there were four ADPLLs on the FPGA arranged in a Cartesian Grid and as such each ADPLL will be referred to using matrix indexing corresponding to their grid location. For each configuration three different modes of operation were examined: Each ADPLL locking to the same 5 MHz external reference, each ADPLL connected to the left and above neighbours in a ``uni-directional'' network and finally a true ADPLL network where all neighbours are connected. For comparison, each configuration gains which had previously been determined to provide the best jitter performance were chosen. The data was captured using an Agilent MSO7054 A at 4 GSa/s. Each point of data is the mean of five 200 microsecond long captures which were then analysed in Matlab, Table \ref{table:b_c_perf} displays the results of this analysis.\\
The first columns of the table relate to the cycle-to-cycle jitter of the system, the difference between sequential rising edges, and the second portion gives the Time Interval Error, the difference between the actual timing of the edge and the ``ideal'' time as set by the reference. This combination of measurements will show how well each design performs the task of staying consistent from cycle to cycle both in relation to itself and the system at large.

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &78.458&74.025&67.779  &146.09&143.70&142.03 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &78.428&72.646&65.665  &146.23&298.49&200.10 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &78.436&73.827&67.648  &235.73&497.60&311.28 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &7.8090&7.8827&6.6272   &17.336&21.151&24.302 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &7.7866&8.1145&7.3598   &17.649&29.962&37.051 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &7.7575&7.7729&6.6962   &30.019&40.577&45.617 \T\\
                \hline
                \B
            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
It is apparently that the combination of the inverter chain DCO and the FPGA clocked phase detector is an ill advised choice, with the system's jitter being an order of magnitude worse than the design using inverter delay based detector. However when the resolution of the detector is then considered, a potential cause for this issue is found. The detector in case two has a resolution of 3.875 nanoseconds in comparison to the 1.2 nanosecond period step of the oscillator, requiring an increase in the loop filter gains. The problems of relatively inaccurate detection and increased gains combine to produce a system that is only able to achieve poor locking performance. In case three then the detector's resolution improves to 0.6 nanoseconds and produces relatively good system performance. This combination does not perform as well as that of case one, but that is attributable to the unrealistic nature of the FPGA clocked design. Both case one and three work well, delivering a level of jitter that is both low yet allows an indication of how impactful variations in architecture or control parameters are to be seen visually on an oscilloscope with appropriate persistence.\\

>>>>

The technical motivation underlying this paper is the creation of an Field Programmable Gate Array (FPGA) based prototyping platform for All Digital Phase Lock Loop (ADPLL) networks. As the creation of Application Specific Integrated Circuits (ASICs) is an expensive and time consuming process, and mistakes made in the design may require the manufacture of a new chip, it is important to ensure that any errors made in the design have been located and addressed before manufacture..

@@

\section{System Architecture}
An ADPLL network, as the name would suggest, is created from a number of ADPLLs that are coupled using digital phase comparators which attempt to measure the phase error between two oscillators, with each non edge node being connected to four neighbours. Figure \ref{fig:adpll_network} illustrates such a system on a small scale, with a number of ADPLLs laid out in a Cartesian grid. The individual ADPLLs, often called distributed ADPLLs as the phase detectors are shared between nodes, are made up of a digitally controllable oscillator, an error combination block and a digital loop filter with the aforementioned digital phase detectors lying between each pair of oscillators.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.25\textwidth]{adpll_network}
    \caption{ADPLL Network Architecture.}
    \label{fig:adpll_network}
    \vspace{0.5cm}
    \includegraphics[width=0.4\textwidth]{dist_adpll}
    \caption{Distributed ADPLL Design.}
    \label{fig:adpll_base}
    \vspace{-0.5cm}
\end{figure}
\subsection{Digitally Controlled Oscillators}
While regular Voltage Controlled Oscillator (VCO) is tuned by the input voltage over a continuous range of values, in a digital system there are a very limited number of voltages representable, most commonly just two levels. As such, using the voltage itself to control an oscillator is not a viable strategy and instead Digitally (or Numerically) Controlled Oscillators (DCO) accept an \textit{n} bit wide control signal that alters the period of the output waveform. While tuning range, centre frequency and linearity apply as in a VCO, a DCO also has a minimum frequency step as a result of the non continuous control values. %TODO WORDING
In combination with the bit width of the control signal, the minimum frequency step limits the range over which the oscillator can be tuned. Frequently the output of the DCO is divided down to allow the control blocks in the feedback path that are clocked on this signal, to run at a lower and thus easier frequency.
\subsection{Loop Filter}
The loop filter is a key aspect of a phase lock loop as without it only the current output of the phase detector could be used to compute the control voltage of the VCO.
In an ADPLL it performs an identical role however, the digital environment results in the traditional loop filter being replaced by a discrete time Proportional Integral (PI) controller, with the integral path of the controller implemented by an accumulator.
\subsection{Error Combiner}
The Error Combiner, as the name suggests, performs a summation of the error signals from the phase detectors lying between any neighbouring oscillator and its neighbours. It is often convenient for this to be performed as a weighted sum, thus avoiding different gain requirements for the loop filter of oscillators in the corners of the grid that only have a pair of neighbours. The ability to change the weights during operation enables ``uni-directional start-up'', which Javiden et. al \cite{javidan2011all} found prevented the system from entering unwanted stable equilibriums warned of in Pratt and Nguyen's seminal paper.
\subsection{Phase Detector}
In a conventional PLL the phase detector measures a value proportional to the difference in phase between a pair of signals, which is then output as a continuous voltage.
A digital phase detector then attempts to do the same by measuring the time difference between fixed reference points in the waveform, which as a digital system deals with square waves, is typically the rising edge of each input to the block.
As in the oscillator, quantisation also plays a role in the behaviour of this block, with the time difference between each rising edge having a minimum possible measurement step.
In distributed ADPLLs the phase detector has dual outputs, each the inverse of the other, in order to feed the correct value to both of the connected error combiners.

\section{FPGA Prototyping}
\subsection{FPGA Restrictions}
The use of an FPGA comes with many restrictions as to how a complex system such as an ADPLL can be designed with the mixed signal blocks, the DCO and phase detectors in particular being curtailed by the lack of transistor level control of the design and layout.\\
Two potential solutions exist which alleviate this problem, and are suited to different frequency ranges and/or goals of the designer. Firstly the clock signal generated by the FPGA's clock distribution block can be used to drive accumulator based oscillators and phase detectors, a technique suitable in two main use cases: The emulation of the performance of an already designed system operating at a proportionally cut down frequency or if the target frequency is low. 
The downside of this approach is that the minimum steps are dictated by the clock frequency of the FPGA, which at frequencies that are not orders of magnitude lower than the FPGA clock will result in coarse resolutions for detector or oscillator, and thus greater jitter seen at the oscillator output.
Accordingly this method only suitable for use at frequencies that are orders of magnitude lower than the maximum obtainable clock frequency of the FPGA's clock manager.\\
The second solution to the problem is more akin to the real world system, and uses the delay through primitive elements such as inverters, which can be deduced from measurements on the FPGA of choice but will vary depending on the layout selected. In the case of the FPGA used for this paper, a Xilinx Artix-7 (XC7A100T-1CSG324C), this delay is in the region of 300 picoseconds but varies depending on the routing between elements. This design is better suited to scenarios where the desired operating frequency is a significant fraction of the maximum usable clock of the FPGA or it is particularly desirable to have asynchronous behaviour in the system as in an ASIC. It is not suited to lower frequency designs as the number of inverters required will run into spacial constraints.
\subsection{Digitally Controlled Oscillators on an FPGA}
There are three key designs that be used to implement a DCO on an FPGA, two relying on the FPGA clock and one using inverter primitives. Each of these designs fulfils a different role in mimicking the behaviour of an ASIC based mixed signal DCO.

@@

\subsection{Phase Detectors on an FPGA}
The two options for replicating the behaviour of a phase detector also employ the same two design principles, with the option better suited to lower frequency signals once again, being driven by the clock generated by the FPGA and an inverter based design better suiting higher frequency systems, where the greater resolution offered is beneficial.\\
A  Sign-Number (SigNum) detector is a common method of performing phase-frequency detection in an ADPLL and is the method that will be discussed in this paper. As the name suggests, this design constitutes two sections, with one determining the sign of the phase difference and the other, its magnitude. The first issue with implementing a phase detector on an FPGA is the issue of metastability, where the output of a circuit element is at an undetermined level, which can occur if both signals were to have edges within a short time of one another or the set-up/hold times of a register are violated. This issue is easily addressed in an ASIC with an arbiter, however, an arbiter is a mixed signal circuit that is not synthesisable on an FPGA.

\subsubsection*{Design A}
The first potential design uses a Finite State Machine (FSM) to determine which edge has occurred first and thus the sign, and a counter that computes the time difference between each rising edge of each signal. This counter is clocked by the FPGA clock, thus giving the system a time resolution of $\frac{1}{F_{\textrm{FPGA}}}$. As with the FPGA driven oscillator, this results in a design that is only suitable when the frequency of operation is well below that of the FPGA clock due to resolution constraints. In order to avoid the problem of metastability, the incoming waveforms can be synchronised to the clock of the FPGA for no penalty beyond the extra clock cycle taken, as this synchronisation performs the same quantisation that would otherwise have occurred in the counter measuring the time difference. This design is better suited for use with the accumulator based oscillators due to the overlapping suitable frequency ranges, however, it can also be used in conjunction with an inverter ring. 
%Important to note is that in the case of the Artix-7 used in this paper, this results in a four times worse phase difference resolution than period resolution which made low jitter operation difficult, but this combination could be made possible by removing eight rather than two inverters for each control code step. %TODO plot this later

\subsubsection*{Design B}
Better suited for use with the inverter based oscillator, is a system that mimics the behaviour of a tapped delay line, working asynchronously to the FPGA clock. As the FPGA clock is not used, and that of the ADPLL cannot be used to measure itself, an unclocked sign detection circuit is required, an example of which can be seen in Figure \ref{fig:segn_pdetdl}. This is nearly identical to sign detection methods used on an ASIC, with the arbitration circuit replaced by a second SR Latch, which alleviates the issue of metastability.\\
A tapped delay line can be emulated on an FPGA through the use of inverter pairs, due to their short and approximately known delay placed between each tap.
The resolution then is the propagation time through the pair, although this will once again depend on the layout specifics, which was approximately 600 picoseconds on an Artix-7. This is significantly lower than the 4 nanoseconds achieved using the previous design and thus more suitable for use with an inverter ring oscillator, as this resolution is better than the time resolution of the oscillator. Figure \ref{fig:num_pdetdl} illustrates the configuration of the circuit used to emulate the function of a delay line that will be used in this paper.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{../new_pdet1}
    \caption{Design B Sign Detection RTL Diagram.}
    \label{fig:segn_pdetdl}
    \vspace{-0.5cm}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{../new_pdet2}
    \caption{Tapped Delay Line Emulation RTL Diagram.}
    \label{fig:num_pdetdl}
    \vspace{-0.5cm}
\end{figure}
\section{Comparison of Designs}
This paper will now examine the performance of a number of combinations of these blocks and the performance thereof, specifically oscillator 1 with phase detector A and oscillator 2 with detectors A \& B. For each test there were four ADPLLs on the FPGA arranged in a Cartesian Grid and as such each ADPLL will be referred to using matrix indexing corresponding to their grid location. For each configuration three different modes of operation were examined: Each ADPLL locking to the same 5 MHz external reference, each ADPLL connected to the left and above neighbours in a ``uni-directional'' network and finally a true ADPLL network where all neighbours are connected. For comparison, each configuration uses loop filter gains which had previously been determined to provide the best jitter performance. The data was captured using an Agilent MSO7054-A oscilloscope at 4 GSa/s. Each point of data is the mean of five 200 microsecond long captures which were then analysed in Matlab, Table \ref{table:b_c_perf} displays the results of this analysis.\\
The first columns of the table relate to the cycle-to-cycle jitter of the system, the difference between sequential rising edges, and the second portion gives the Time Interval Error, the difference between the actual timing of the edge and the ``ideal'' time as set by the reference. This combination of measurements will show how well each design performs the task of staying consistent from cycle to cycle both in relation to itself and the system at large.

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &78.458&74.025&67.779  &146.09&143.70&142.03 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &78.428&72.646&65.665  &146.23&298.49&200.10 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &78.436&73.827&67.648  &235.73&497.60&311.28 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &7.8090&7.8827&6.6272   &17.336&21.151&24.302 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &7.7866&8.1145&7.3598   &17.649&29.962&37.051 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &7.7575&7.7729&6.6962   &30.019&40.577&45.617 \T\\
                \hline
                \B
            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
It is apparently that the combination of the inverter chain DCO and the FPGA clocked phase detector is an ill advised choice, with the system's jitter being an order of magnitude worse than the design using inverter delay based detector. However when the resolution of the detector is then considered, a potential cause for this issue is found. The detector in case two has a resolution of 3.875 nanoseconds, as 258 MHz is the maximum FPGA clock frequency that can be used with this design, in comparison to the 1.2 nanosecond period step of the oscillator, requiring an increase in the loop filter gains. The problems of relatively inaccurate detection and increased gains combine to produce a system that is only able to achieve poor locking performance. In case three then the detector's resolution improves to 0.6 nanoseconds and produces relatively good system performance. This combination does not perform as well as that of case one, but that is attributable to the unrealistic nature of the FPGA clocked design. Both case one and three work well, delivering a level of jitter that is both low yet allows an indication of how impactful variations in architecture or control parameters are to be seen visually on an oscilloscope with appropriate persistence.\\
